---
title: "Alcohol vs Seat choice"
author: "April Galvan"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

Visually the plot shows a significant difference between the back row and the middle row. Also shows an even bigger significant difference between the back row and front row.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

According to this chart, the back row drinks 8.5 more drinks than the middle and front rows. Middle row drinks 3.3 drinks per week and the front row drinks 1.7 per week. It's reasonable to assume that they are not drinking the same amount of alcohol per week.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The p value represents the chances of getting a result like we just obtained if the null hypothesis is actually true. Since the result is so small, I am going to reject the null hypothesis.

## Conclusions



